### 2013-12-03 proposal/proposal/chapter5.tex
changes

\setcounter{chapter}{3}
\chapter{Conclusion and Future Work}\label{sec:conclusionfuturework}
In this chapter, we describe the phases of our plan for exploring the research challenges and investigating the research issues identified in Chapter 4. This chapter also includes research methodology and future publication plan.

@@

In this report, we proposed a cooperative game theory-based model
for the aggregation of web services within communities. The goal
of our services is to maximize efficiency by collaborating and
forming stable coalitions. Our method considers stability and
fairness for all web services within a community and offers an
applicable mechanism for membership requests and selection of web
services. The ultimate goal is to increase revenue by improving
user satisfaction, which comes from the ability to perform more
tasks with high quality. Simulation results show that our,
polynomial in complexity, approximation algorithms provide web
services and community owners with applicable and near-optimal
decision making mechanisms.

@@

\indent The future goals in this PhD research work mainly consists of:

\begin{itemize}
\item Analysing other cooperative solution concepts such as Kernel and Nucleolus where payoff division is guaranteed to exist but may have optimal results.
\item Applying Weighted Voting Games (WCG) type of valuation function in our scenarios, Developing a multiple weighted algorithm to find best coalition structures satisfying different weights on each community.
\item Implementing Q-learning and reinforcement learning technique and also a tic-tac-toe based repeated game technique for individual Web Service decision making process, in long term and repeated game scenarios.
\item Developing an approximation algorithm for shapely value payoff distribution vector in community of service setting.
\item Developing a community membership algorithm technique for our agents in "incomplete information" settings.
\item Developing an open source, Java based Tool, with UI for solving Core and Shapely solution concepts based on different input valuation functions.
\end{itemize}

    \begin{figure}
                \begin{center}
%                \includegraphics[width=16cm, height=22cm]{timeline/timetable.pdf}\label{Timetable}
                \includegraphics[width=16cm]{timeline/timetable.pdf}\label{Timetable}
                \caption{Research milestones and timeline}
                \end{center}
    \end{figure}

>>>>

\setcounter{chapter}{3}
\chapter{Conclusion and Future Work}\label{sec:conclusionfuturework}
In this chapter, we describe the phases of our plan for exploring
the research challenges and investigating the research issues
identified in Chapter 3. This chapter also includes research
methodology and future publication plan.

@@

In this report, we presented research problems and questions we
aim to address in the thesis and proposed some preliminary results
about a cooperative game theory-based model for the aggregation of
web services within communities. The goal of our services is to
maximize efficiency by collaborating and forming stable
coalitions. Our method considers stability and fairness for all
web services within a community and offers an applicable mechanism
for membership requests and selection of web services. The
ultimate goal is to increase revenue by improving user
satisfaction, which comes from the ability to perform more tasks
with high quality. Simulation results show that our approximation
algorithms are polynomial in complexity and provide web services
and community owners with applicable and near-optimal decision
making mechanisms.

@@

\indent The future goals in this Ph.D. research work are:

\begin{itemize}
\item Analyzing other cooperative solution concepts such as Kernel
and Nucleolus where payoff division is guaranteed to exist and may
have optimal results.

\item Applying other valuation function in our scenarios using for
instance Weighted Voting Games (WCG) in order to develop a
multiple weighted algorithm to find best coalition structures
satisfying different weights on each community.

\item Analyzing the impact of Q-learning and reinforcement
learning on the performance of our model.

\item Developing an approximation algorithm for shapely value
payoff distribution vector in community setting.

\item Developing a community membership algorithm technique for
our agents in "incomplete information" settings.

%\item Developing an open source, Java based Tool, with UI for
%solving Core and Shapely solution concepts based on different
%input valuation functions.
\end{itemize}

    \begin{figure}
                \begin{center}
%                \includegraphics[width=16cm, height=22cm]{timeline/timetable.pdf}\label{Timetable}
                \includegraphics[width=16cm]{timeline/timetable1.eps}\label{Timetable}
                \caption{Research milestones and timeline}
                \end{center}
    \end{figure}
